Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-19 Supplemental Material B - Coding Protocol/Supplemental Material B - Coding Protocol.tex
coding protocol filled

\name{Documentation: \par Coding Protocol}
\tagline{For: `The Migration Experience: A Conceptual Framework and Systematic Scoping Review of Psychological Acculturation'}
\made{February 20 2021}
%%\logo{6.8cm}{images/MJ Research Design}
%%\logo{6.8cm}{example-image}
\logo{6.8cm}{images/rugLogoBlack}
%\logo{6.8cm}{images/rugLogoBlackMasked}

\docinfo{%
  % can add more \addedtopeople
  \madeby{Jannis Kreienkamp}{j.kreienkamp@rug.nl}{February 20, 2021}
  \addedto{Laura F. Bringmann}
  \addedto{Raili F. Engler}
  \addedto{Peter de Jonge}
  \addedto{Kai Epstude}
  %\madeby{[masked for peer review]}{[masked for peer review]}{February 20, 2021}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
}

\purpose{
	This protocol document lays out detailed information for coders of the (included) manuscripts. This document serves as an instructive manual to the coders and documents the operationalizations of the coded variables. The systematic review produced three literature databases that aim to capture the status quo of the (1) theoretical, (2) methodological, and (3) empirical literature on psychological acculturation. The coding procedures (i.e., data extraction) for each dataset are documented in the following document protocol.
} % add a short description of the purpose for this protocol

@@

%% Provide the file name containing the sidebar contents as an optional parameter to \need.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \need title in the "main" bar.
\need[margins/materials]{Theoretical Literature}

\category{1}{Bibliographic Information}

\step{Theory}{What is the name of the theory?}{Bibliographic Information}
\textit{Whenever possible record the name of the theory chosen by the authors themselves.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{Source}{Add the full APA 7 formatted citation of the theoretical manuscript that is being coded.}{Bibliographic Information}
\textit{Example format: Author, A. A., \& Author, B. B. (Year). Title of the work. Source where you can retrieve the work. DOI (or URL) if available.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\step{CitationKey}{Add BibTeX citation key for the theoretical manuscript.}{Bibliographic Information}
\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: Author2019}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\clearpage
\vspace*{1em}

\category{2}{Screening}

\step{MissingABCD}{Whether the experience aspects (affect, behavior, cognition, and desire) are coded.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{coded \dotfill[0]}
	\item \makebox[5cm]{missing \dotfill[1]}
\end{itemize}
\divider

\marginpar{
\vspace{2em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
\bottomrule
\end{tabular*}
}

\divider
\step{NoteMissing}{If experience aspects (affect, behavior, cognition, desire) not coded, provide the reason for missing coding.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not theory \dotfill[6]}
	\item \makebox[5cm]{thesis not accessible \dotfill[7]}
	\item \makebox[5cm]{article not accessible \dotfill[8]}
	\item \makebox[5cm]{book not accessible \dotfill[9]}
	\item \makebox[5cm]{chapter not accessible \dotfill[10]}
	\item \makebox[5cm]{poster not accessible \dotfill[11]}
\end{itemize}
\divider

\step{Comment}{Any necessary comments of the coder.}{Screening}
\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{3}{Theory Information}

\step{Summary}{A short summary of the theoretical work.}{Theory Information}
\textit{This summary ideally includes the sections that were relevant to the experience aspect (affect, behavior, cognition, desire) coding.}
\vspace{1.5em}

\rule{10cm}{\rulewidth}\vspace{0.75em}
\rule{10cm}{\rulewidth}\vspace{0.75em}
\rule{10cm}{\rulewidth}\vspace{0.75em}
\ruleandname{character string}{10cm}
\divider

\clearpage
\vspace*{2em}

\step{FrameworkTheoryModel}{Type of theoretical work, as identified by the author.}{Theory Information}
\textit{Please code the term that is being used by the author(s).}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{conceptualization \dotfill[1]}
	\item \makebox[5cm]{framework \dotfill[2]}
	\item \makebox[5cm]{theory \dotfill[3]}
	\item \makebox[5cm]{model \dotfill[4]}
\end{itemize}
\divider

\step{GeneralAspect}{Whether the theoretical work is about acculturation in general or whether it conceptualizes a particular aspect of acculturation.}{Theory Information}
\textit{Is acculturation in general being considered or do the authors focus on a single aspect of acculturation, such as theories on labor market integration.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{general \dotfill[1]}
	\item \makebox[5cm]{aspect \dotfill[2]}
\end{itemize}
\divider

\step{Target}{If aspect is targeted, what is the target of the theoretical work?}{Theory Information}
\textit{Example aspects might be theoretical works that exclusively focus on labor market integration or identity development.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\category{4}{Experience}
\marginpar{
\vspace{3em}
Selected Affect Concept Examples:
\begin{itemize}
    \item loneliness
    \item feeling at home
    \item satisfaction with life
    \item pride
    \item comfortableness
    \item joy
    \item ease
    \item well-being
    \item worry
    \item trust
\end{itemize}
}

\step{Affect}{Whether the theoretical conceptualization included affect.}{Experience}
\textit{To identify whether the author(s) included affective experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of affect. Please consider affect at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
\textbf{Operationalization:} the authors might also include affective conceptualizations in their descriptions of experiences, such as `a person feels' or `a person enjoys'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{3em}
Selected Behavior Concept Examples:
\begin{itemize}
    \item language use
    \item civic participation (voting, ...)
    \item performance (work, ...)
    \item media consumption
    \item education
    \item peer contacts
    \item food consumption
    \item cultural habits (holidays ...)
    \item delinquency
    \item marriage
\end{itemize}
}

\step{Behavior}{Whether the theoretical conceptualization included behavior(s).}{Experience}
\textit{To identify whether the author(s) included behavioral experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of behaviors. Please consider behaviors at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their descriptions of experiences, such as `a person does' or `a person works'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Cognition Concept Examples:
\begin{itemize}
    \item ethnic identification
    \item cultural values
    \item acculturation orientation
    \item preferences (food, friends, ...)
    \item knowledge
    \item importance ratings
    \item inner thought language
    \item perceived obligations
    \item beliefs
    \item stereotypes
\end{itemize}
}

\step{Cognition}{Whether the theoretical conceptualization included cognition(s).}{Experience}
\textit{To identify whether the author(s) included cognitive experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of cognitions. Please consider cognitions at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
\textbf{Operationalization:} the authors might also include cognitive conceptualizations in their descriptions of experiences, such as `a person thinks' or `a person prefers'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Desire Concept Examples:
\begin{itemize}
    \item competence
    \item independence
    \item self-coherence
    \item belonging
    \item achievement
    \item justice
    \item growth
    \item respect
    \item acceptance
    \item identity continuity
\end{itemize}
}

\step{Desire}{Whether the theoretical conceptualization included desire(s).}{Experience}
\textit{To identify whether the author(s) included motivational experiences in their theoretical conceptualization, you can examine the author(s)' theoretical axioms, theorems, and model elements for self-identified mentions of desires. Please consider desires at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
\textbf{Construct:} the authors might refer to desire constructs such as `needs' or `goals'.\\
\textbf{Concept:} the authors might refer to desire concepts, such as `belonging' or `competence'.\\
\textbf{Operationalization:} the authors might also include motivational conceptualizations in their descriptions of experiences, such as `a person wants' or `a person needs'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\category{5}{Data Collection}

\step{SourceType}{Whether the theoretical conceptualization is based on theoretical reasoning or empirical investigations.}{Data Collection}
\textit{Is the theoretical reasoning focused on past theoretical work or do the authors build a theoretical conceptualization based on (qualitative) investigations (e.g., grounded theory).}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{theoretical \dotfill[1]}
	\item \makebox[5cm]{empirical \dotfill[2]}
\end{itemize}
\divider

\category{6}{Focus}

\step{Time}{Whether the conceptualization of acculturation is dynamic or static.}{Focus}
\textit{Do the authors self-identify the theory as a dynamic process (e.g., `process,' `development,' `longitudinal,' `temporal,' `dynamic') or a static outcome (e.g., `static,' `outcome,' `markers,' `consequence')}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{static \dotfill[1]}
	\item \makebox[5cm]{dynamic \dotfill[2]}
\end{itemize}
\divider

\marginpar{
\need{Methods Dataset}
\resizebox{7cm}{!}{
    % For organization, I like to keep the actual card in a separate file:
    \input{Supplemental Material A - Coding Protocol/margins/FactSheetMethodological}
    }
}
\need{Methodological Literature}
\category{1}{Bibliographic Information}

\step{Scale}{What is the name of the scale?}{Bibliographic Information}
\textit{Whenever possible record the name of the scale chosen by the authors themselves.}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{Source}{Whether the scale was added as part of one of the past methodological reviews or through our own review of the empirical literature.}{Bibliographic Information}
\textit{Indicate whether the scale was included in one or multiple of the past methodological reviews or was added from our own review.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{Celenk2011 \dotfill[1]}
	\item \makebox[5cm]{Matsudaira2006 \dotfill[2]}
	\item \makebox[5cm]{Wallace2010 \dotfill[3]}
	\item \makebox[5cm]{own review \dotfill[4]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\step{CitationKey}{Add BibTeX citation key for the theoretical manuscript.}{Bibliographic Information}
\textit{The citation key can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: Author2019}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\step{APACite}{Add the full APA 7 formatted citation of the theoretical manuscript that is being coded.}{Bibliographic Information.}
\textit{Example format: Author, A. A., \& Author, B. B. (Year). Title of the work. Source where you can retrieve the work. DOI (or URL) if available.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\step{DOI}{Add Digial Object Identifier (DOI).}{Bibliographic Information}
\textit{The doi can be found in the bibliography manager (either in the shared Mendeley Library or the 'references.bib' file.)}
\textit{\newline Example format: 10.prefix/suffix}
\vspace{1.5em}
\ruleandname{character string}{5cm}
\divider

\category{2}{Screening}

\step{Coded}{Whether the experience aspects (affect, behavior, cognition, and desire) are coded.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{missing \dotfill[0]}
	\item \makebox[5cm]{coded \dotfill[1]}
\end{itemize}
\divider

\marginpar{
\vspace{1.4em}
Missingness Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & manuscript is in a language other than English. \\
2 & rural-urban, second generation \\
3 & focus on dominant group \\
4 & purely descriptive studies and replications in migrant populations. E.g., mental health of migrant group in general. \\
5 & migration status, length of residence  \\
6 & only discusses theory of others. \\
7 & not accessible via library services \\
8 & not accessible via library services \\
9 & not accessible via library services \\
10 & not accessible via library services \\
11 & not accessible via library services \\
12 & not accessible via library services \\
\bottomrule
\end{tabular*}
}

\divider
\step{MissingNote}{If experience aspects (affect, behavior, cognition, desire) not coded, provide the reason for missing coding.}{Screening}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{not English \dotfill[1]}
	\item \makebox[5cm]{not migration \dotfill[2]}
	\item \makebox[5cm]{not migrant \dotfill[3]}
	\item \makebox[5cm]{not acculturation \dotfill[4]}
	\item \makebox[5cm]{not ABCD \dotfill[5]}
	\item \makebox[5cm]{not measured \dotfill[6]}
	\item \makebox[5cm]{items not accessible \dotfill[7]}
	\item \makebox[5cm]{thesis not accessible \dotfill[8]}
	\item \makebox[5cm]{article not accessible \dotfill[9]}
	\item \makebox[5cm]{book not accessible \dotfill[10]}
	\item \makebox[5cm]{chapter not accessible \dotfill[11]}
	\item \makebox[5cm]{poster not accessible \dotfill[12]}
\end{itemize}
\divider

\step{Comment}{Any necessary comments by the coder.}{Screening}
\textit{This can include additional information about the format and content of the theoretical work, as well as information on the missingness or accessibility.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{3}{Scale Information}

\step{Item}{Extract all available items of the scale.}{Scale Information}
\textit{List all items of the scale as they are presented in the manuscript. If scoring is inconsistent consider adding basic scoring information to the items. Please number the items for clarity.}
\vspace{1.5em}
\par
\hspace*{1pt}1. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}2. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}3. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}4. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}5. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}6. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}7. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}8. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}9. \\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}... .\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}\textit{N}.\\\rule[0.95em]{6cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip-\ruleandnamegap}
\noindent{\namefont character string}\par
\divider

\step{NItem}{Number of items in the scale.}{Scale Information}
\textit{The total number of items should match the highest numbering in the `Item' variable. If that is not the case please explain in the `Note' section.}
\vspace{1.5em}
\par
\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
\noindent{\namefont numeric}\par
\divider

\step{NSubScales}{Number of sub-scales identified by the authors.}{Scale Information}
\textit{If multiple sets of sub-scales are proposed please elaborate in the `Note' section.}
\vspace{1.5em}
\par
\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
\noindent{\namefont numeric}\par
\divider

\clearpage
\vspace*{2em}

\step{ResponseRange}{Number of response options.}{Scale Information}
\textit{If multiple response ranges are used please specify in the `Note' section.}
\vspace{1.5em}
\par
\rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \hspace{1pt} \rule{0.5cm}{\rulewidth} \par
\vspace{\dimexpr-\baselineskip+\ruleandnamegap}
\noindent{\namefont numeric}\par
\divider

\step{ResponseRangeAnchors}{List the anchors associated with the reported the response range.}{Scale Information}
\textit{If multiple sets of anchors are used please specify in the `Note' section.\\ Example format for range \{-2, 2\}:}
\vspace{1.5em}
\par
\hspace*{1pt}\textit{\textcolor{body}{-2: very negative}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{1pt}\textit{\textcolor{body}{-1: negative}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{4pt}\textit{\textcolor{body}{0: neutral}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{4pt}\textit{\textcolor{body}{1: positive}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\hspace*{4pt}\textit{\textcolor{body}{2: very positive}}\\\rule[0.95em]{6cm}{\rulewidth}\\
\vspace{\dimexpr-\baselineskip-\ruleandnamegap}
\noindent{\namefont character string}\par
\divider

\step{Note}{Any necessary coder comments about the scale.}{Scale Information}
\textit{Any notes on the scale, including the structure of the scale (e.g., names of the sub-scales).}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider

\category{4}{Experience}
\marginpar{
\vspace{3em}
Selected Affect Concept Examples:
\begin{itemize}
    \item loneliness
    \item feeling at home
    \item satisfaction with life
    \item pride
    \item comfortableness
    \item joy
    \item ease
    \item well-being
    \item worry
    \item trust
\end{itemize}
}

\step{Affect}{Whether the scale includes affect.}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of affect. Please consider affect at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `affect' or `affective' directly.\\
\textbf{Construct:} the authors might refer to affective constructs such as `emotion' or `mood'.\\
\textbf{Concept:} the authors might refer to affective concepts such as individual emotions, including `pride' or `loneliness'.\\
\textbf{Operationalization:} the authors might also include affective conceptualizations in their items, such as `I feel ...' or `I enjoy ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{3em}
Selected Behavior Concept Examples:
\begin{itemize}
    \item language use
    \item civic participation (voting, ...)
    \item performance (work, ...)
    \item media consumption
    \item education
    \item peer contacts
    \item food consumption
    \item cultural habits (holidays ...)
    \item delinquency
    \item marriage
\end{itemize}
}

\step{Behavior}{Whether the scale includes behavior(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of behaviors. Please consider behaviors at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `behavior' or `behavioral' directly.\\
\textbf{Construct:} the authors might refer to behavioral constructs such as `activities' or `habits'.\\
\textbf{Concept:} the authors might refer to behavioral concepts, such as `language use' or `media consumption'.\\
\textbf{Operationalization:} the authors might also include behavioral conceptualizations in their items, such as `I do ...' or `I speak ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Cognition Concept Examples:
\begin{itemize}
    \item ethnic identification
    \item cultural values
    \item acculturation orientation
    \item preferences (food, friends, ...)
    \item knowledge
    \item importance ratings
    \item inner thought language
    \item perceived obligations
    \item beliefs
    \item stereotypes
\end{itemize}
}

\step{Cognition}{Whether the scale includes cognition(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of cognitions. Please consider cognitions at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `cognition' or `cognitive' directly.\\
\textbf{Construct:} the authors might refer to cognitive constructs such as `knowledge' or `memories'.\\
\textbf{Concept:} the authors might refer to cognitive concepts, such as `cultural values' or `ethnic identification'.\\
\textbf{Operationalization:} the authors might also include cognitive conceptualizations in their items, such as `I think ...' or `I prefer ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\marginpar{
\vspace{3em}
Selected Desire Concept Examples:
\begin{itemize}
    \item competence
    \item independence
    \item self-coherence
    \item belonging
    \item achievement
    \item justice
    \item growth
    \item respect
    \item acceptance
    \item identity continuity
\end{itemize}
}

\step{Desire}{Whether the scale includes desire(s).}{Experience}
\textit{To identify whether the author(s) included affective experiences in their scale, you can examine the scale description, the (sub-)scale labels, as well as items for self-identified mentions of desires. Please consider desires at the following three levels of abstraction:\\
\textbf{Aspect:} the authors might refer to `desire' or `motivational' directly.\\
\textbf{Construct:} the authors might refer to desire constructs such as `needs' or `goals'.\\
\textbf{Concept:} the authors might refer to desire concepts, such as `belonging' or `competence'.\\
\textbf{Operationalization:} the authors might also include motivational conceptualizations in their items, such as `I want ...' or `I need ...'.}
\vspace{0.5em}
\begin{itemize}
	\item \makebox[5cm]{included \dotfill[1]}
	\item \makebox[5cm]{not included \dotfill[–]}
\end{itemize}
\divider

\clearpage
\vspace*{2em}

\marginpar{
\vspace{1em}
Complexity Explanations

\begin{tabular*}{6.2cm}{>{\centering\arraybackslash}p{0.08\linewidth} 
>{\raggedright\arraybackslash}p{0.76\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
1 & focused on a concept that includes multiple aspects (e.g., satisfaction, distress) \\
2 & aspects included as parts of a scale \\
3 & aspects measured as independent conceptualizations of acculturation \\
4 & aspects included as part of a review of multiple conceptualizations \\
N/A & only one aspect was included  \\
\bottomrule
\end{tabular*}
}

>>>>

\name{Documentation: \par Coding Protocol}
\tagline{For: `Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies'}
\made{March 10 2023}
%%\logo{6.8cm}{images/MJ Research Design}
%%\logo{6.8cm}{example-image}
\logo{6.8cm}{images/rugLogoBlack}
%\logo{6.8cm}{images/rugLogoBlackMasked}

\docinfo{%
  % can add more \addedtopeople
  \madeby{Jannis Kreienkamp}{j.kreienkamp@rug.nl}{March 10, 2023}
  \addedto{Maximilian Agostini}
  \addedto{Laura F. Bringmann}
  \addedto{Peter de Jonge}
  \addedto{Kai Epstude}
  %\madeby{[masked for peer review]}{[masked for peer review]}{February 20, 2021}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
  %\addedto{[masked for peer review]}
}

\purpose{
	The purpose of this coding protocol is to assess the goal-directedness of participants' free-text responses regarding their main goal during interactions with outgroup members. The coding will capture two dimensions: practical needs and underlying psychological needs. Two independent coders will evaluate each response, and the dimensions will be assessed separately to ensure the validity and reliability of the coding process.
} % add a short description of the purpose for this protocol

@@

%% Provide the file name containing the sidebar contents as an optional parameter to \need.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \need title in the "main" bar.
\need[margins/materials]{Goal Directedness}

\category{1}{Introduction}

The goal of this coding protocol is to assess the goal-directedness of free-text responses obtained from recent migrants regarding their interactions with outgroup members. Each coder should independently read and analyze each free-text response. For each response, it is your task to determine whether the response presents a practical need and whether it presents a psychological need. You will be asked to assign a code to each dimension based on the presence or absence of the respective need type. We will first explain the coding procedure and will then provide more detailed information on the coding criteria for each dimension.

\vspace{1em}

\category{2}{Coding Procedure}

\begin{enumerate}
    \item Familiarize yourself with the research objectives: Gain a clear understanding of the study's goals and the specific practical and psychological needs, as well as non-goal-directed actions. This understanding will guide the coding process.
    \item Read and understand the research question prompt: Review the survey question that asks participants about their main goal during the interaction. Ensure a thorough understanding of the wording and context to accurately identify responses that indicate underlying needs.
    \item Assign a rating for each dimension (0, 1, or 2) based on the criteria provided.
    \item Rate each dimension independently without being influenced by the rating given to the other dimension.
    \item Use the examples provided as references, but do not limit your assessment to these examples alone.
    \item If a response contains multiple goals, consider the most prominent or emphasized goal in the rating.
    \item In case of ambiguity or uncertainty, code conservatively and opt for a lower rating.
    \item Document your ratings and any notes or comments regarding challenging cases or exceptional responses within the \textit{comment} field.
    \item Regular communication with the research team is encouraged to clarify any uncertainties and maintain consistency in coding.
\end{enumerate}

\newpage
\vspace*{3em}
\textbf{Coding Agreement and Disagreement:}
\begin{itemize}
    \item After coding all responses, we compare the codes assigned by each coder.
    \item The PI will calculate the inter-coder reliability using appropriate statistical measures (e.g., Cohen's kappa) to determine the agreement between coders.
    \item The coders will resolve any disagreements through discussion and consensus until a final set of codes is reached.
    \item If necessary, we will refine the coding protocol based on the discussion and repeat the coding process to ensure consistency and validity.
\end{itemize}

\vspace{1em}

\category{3}{Coding Criteria}

\step{practical\_need}{Practical Needs Dimension}{needs}
\textit{Practical needs refer to specific, tangible goals or tasks that participants aimed to accomplish during the interaction. These instrumental goals are usually observable, concrete, and often centered on external outcomes. Individuals strive to fulfill these needs to navigate their daily lives efficiently and achieve desired results. Examples of practical needs include engaging in activities such as acquiring resources, completing tasks, and addressing immediate challenges. These needs are closely tied to instrumental and utilitarian considerations, highlighting the pursuit of external rewards, resource acquisition, or problem-solving. It is your task to assess the extent to which the free-text response captures a practical need. Practical needs can include activities such as getting coffee together, working on an assignment, discussing a project, or seeking information.}\\
\vspace{0.5em}
\textit{\textbf{Options:}} \\
\textit{Either there is no practical need to be identified (1), a vague or general mention of a practical need without specific details (2), or a clear mention of a practical need (3).}\\
\vspace{0.5em}
\textit{\textbf{Additional clarification no practical need:}}\\
\textit{Given that many aspects of the human life a driven by needs or at least are recalled or perceived as need-driven, it can be difficult to identify situational reports that do not include a practical need, motive, or goal. Examples of responses that are not goal-directed would be:
\begin{itemize}[nosep]
    \item[--] "I wasn't seeking any particular outcome, I simply wanted to be present in the moment and enjoy the interaction."
    \item[--] "There wasn't a specific objective I aimed to achieve, I just wanted to see where the conversation would take us."
    \item[--] "I wasn't focused on achieving a particular outcome, my intention was to engage in a spontaneous and genuine conversation."
\end{itemize}
These examples reflect a lack of specific goals or intentions during intergroup interactions. These examples express a more open and non-directed approach, where the primary focus was on the process of interaction itself rather than aiming for specific outcomes or results.}

\vspace{0.5em}
\textit{\textbf{Codes:}}
\vspace{0.5em}

\marginpar{
\vspace{-4em}
Practical Need Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
0 & ``We just exchanged greetings and went our separate ways.'' \\
1 & ``We had a task to complete.'' \\
2 & ``We met to discuss the upcoming presentation.'' \\
\bottomrule
\end{tabular*}
}
\begin{itemize}
	\item \parbox[t]{6cm}{No practical need \dotfill[0]}
	\item \parbox[t]{6cm}{Vague or general mention \dotfill[1]}
    \item \parbox[t]{6cm}{Clear mention \dotfill[2]}
\end{itemize}

\vspace{1em}
\divider

\newpage
\vspace*{3em}
\divider
\vspace{1em}

\step{psychological\_need}{Psychological Needs Dimension}{needs}
\textit{Psychological needs refer to underlying motives or desires that are more abstract and relate to personal fulfillment and well-being. In contrast to practical needs, psychological needs delve into the subjective and internal aspects of human experiences. These needs pertain to emotions, social connections, and cognitive processes, reflecting individuals' quest for personal growth, well-being, and thriving in social relationships. It is your task to assess the extent to which the free-text response captures an underlying psychological need. Psychological needs can include motives such as sharing and bonding, competence and mastery, feeling valued or respected, or seeking emotional support.\\
\vspace{0.5em}
\textbf{Options:} \\
Similar to the practical need coding, responses might either include no underlying psychological need identified (1), include a vague or general mention of a psychological need without specific details (2), or present a clear mention of a psychological need (3).\\
\vspace{0.5em}
\textbf{Additional clarification no psychological need:}\\
Similar to the practical needs, it can be difficult to identify situational reports that do not include a any underlying psychological need, motive, or goal. Examples of responses that are not goal-directed would be:
\begin{itemize}[nosep]
    \item[--] "I didn't have any specific expectations or goals in mind, I just wanted to see how the conversation would unfold."
    \item[--] "I didn't have a specific goal in mind, I was open to any potential insights or connections that might emerge."
\end{itemize}
These examples reflect a lack of specific goals or intentions during intergroup interactions. If in doubt, try to code conservatively (i.e., try to not infer a need that might not be present) and make a comment if necessary.
}
\vspace{0.5em}
\textit{\textbf{Codes:}}
\vspace{0.5em}

\marginpar{
\vspace{-4em}
Psychological Need Explanations

\begin{tabular*}{6cm}{>{\raggedright\arraybackslash}p{0.03\linewidth} 
>{\raggedright\arraybackslash}p{0.75\linewidth}}
%\begin{tabular}
\toprule
\# & Examples / Explanation\\
\midrule
0 & ``I just wanted to pass the time.'' \\
1 & ``I wanted to connect with someone.'' \\
2 & ``I wanted to share experiences and build rapport.'' \\
\bottomrule
\end{tabular*}
}
\begin{itemize}
	\item \parbox[t]{8.5cm}{No psychological need \dotfill[0]}
	\item \parbox[t]{8.5cm}{Vague or general mention \dotfill[1]}
    \item \parbox[t]{8.5cm}{Clear mention \dotfill[2]}
\end{itemize}

\vspace{1em}
\divider
\vspace{1em}

\step{Comment}{Any necessary comments of the coder.}{context}
\textit{This can include additional information about ambiguous, uncertain, or exceptional codings.}
\vspace{1.5em}
\ruleandname{character string}{10cm}
\divider
